The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-11-01 manuscript.Rmd
add institution contribution table

Marine invertebrates are underrepresented in iDigBio and OBIS given their diversity. We compared the total number of species represented in iDigBio and OBIS for each kingdom to the total described diversity based on the WoRMS estimates[@WorMS-stats]. Records in the databases are biased towards vertebrates: while vertebrates represent  `r total_vert_prop`% of the global diversity, they represent `r idigbio_vert_prop`% and `r obis_vert_prop`% of the species in iDigBio and OBIS respectively (Fig. \@ref(fig:kingdom-diversity-plot)). Additionally, the median number of specimens in iDigBio per species ranges between `r kng_medians %>% filter(sub_kingdom=="animalia") %>% pull(rg)` for invertebrate phyla, but is `r kng_medians %>% filter(sub_kingdom=="animalia - vertebrates") %>% pull(rg)` for vertebrates.

>>>>

```{r records-table, results='asis'}
print.xtableList(institution_contributions, colnames.format = "multiple",
                 booktabs = TRUE, include.rownames = FALSE,
                 table.placement = "!ht")
```

Marine invertebrates are underrepresented in iDigBio and OBIS given their diversity. We compared the total number of species represented in iDigBio and OBIS for each kingdom to the total described diversity based on the WoRMS estimates[@worms-stats]. Records in the databases are biased towards vertebrates: while vertebrates represent  `r total_vert_prop`% of the global diversity, they represent `r idigbio_vert_prop`% and `r obis_vert_prop`% of the species in iDigBio and OBIS respectively (Fig. \@ref(fig:kingdom-diversity-plot)). Additionally, the median number of specimens in iDigBio per species ranges between `r kng_medians %>% filter(sub_kingdom=="animalia") %>% pull(rg)` for invertebrate phyla, but is `r kng_medians %>% filter(sub_kingdom=="animalia - vertebrates") %>% pull(rg)` for vertebrates.
